---
title: "Coffee Package"
author: "Erin Bugbee, Sarah Fringer, Amy Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Coffee Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Sentiment Analysis for Twitter Data  

> "Twitter is what’s happening in the world and what people are talking about right now."  
- twitter.com

To view Twitter, visit <https://about.twitter.com/>

This package contains functions that allows users to scrape twitter data and conduct sentiment analysis of the tweets on different coffee shops. 

The coffee package has five functions suited for this purpose: 

  * get_tweets()
  * clean_tweets() 
  * make_wordcloud()
  * make_bar_graph()
  * make_cat_graph() 

## Scraping Twitter Data 

### 1) get_tweets
This function allows users to save tweets that contain a specified keyword into a .csv file named keyword_tweets.csv (replace "keyword" for the word you want to search).

The get_tweets() function takes in two arguments, the keyword and the number of tweets. The default number of tweets saved is 500.  

In the example image below, the user has searched for the keyword "starbucks" and this is the output .csv file. 

### 2) clean_tweets
This function allows users to clean tweets from the .csv file previously saved from the get_tweets() function and then save these cleaned tweets into a new file named clean_keyword_tweets.csv.

Cleaning the tweets includes removing numbers, hashtags, urls, "RT"'s, twitter usernames, punctuation, emojis, new lines, and leading and trailing white space. It also makes all the tweets lowercase. 

The clean_tweets() function take in one argument, the .csv file created from get_tweets(). 

## Sentiment Analysis Visualizations 

### 3) make_wordcloud
_A wordcloud is used to highlight popular words based on the frequency of use and prominence in the tweets._

This function allows users to make a word cloud given a .csv file from the clean_tweets() function. 

The make_wordcloud() function takes in two arguments, the clean .csv file and the number of words included in the word cloud. 

### 4) make_bar_graph
This function allows users to make a sentiment bar graph given a .csv file from the clean_tweets() function. 

The make_bar_graph() function takes in one argument, the clean .csv file. 

### 5) make_cat_graph 
This function allows users to make emotional categorical bar graphs given a .csv file from the clean_tweets() function. 

The make_cat_graph() function takes in one argument, the clean .csv file. 

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
